Adaptative neighbouring methods applied to telephonic base stations

### 2024-09-03 article.tex
transition sentences

        Firstly, only one provider is considered because a BS from provider $x$ can't be considered as a neighbour of BS from provider $y$.
        Consequently, we have chosen \emph{Orange} because it is the one that has the largest number of BS.

@@

\section{Overview of use methods\label{sec:overview}}
    \subsection{Finding potential neighbours}
        When looking for neighbours, at first, a list of potential neighbours for each point is necessary.
        For that, a neighbouring graph is constructed where $P$ is the set of all points and each edge in this graph represents a neighbouring relation.

        \subsubsection{$k$-NN graph}
            The most intuitive method is to connect each point to its $k$ nearest neighbours, where $k \in \mathbb{N}^*$ is a parameter to be set up.

@@

    \subsection{Finding real neighbours}
        For the purpose of our experiments, i.e. finding BS neighbours, the previously presented methods are not sufficient to find real neighbours.
        As a consequence, some neighbouring connexions needs to be suppressed \cite{patent_neighs}.
        \subsubsection{Distance criterion}
            A BS does not have an infinite coverage area.
            As a consequence, each edge in $U$ that is longer than a certain value, called \emph{max\_distance}, is suppressed.

@@

    \subsection{Density-based clustering methods}
        \subsubsection{DBScan}
            DBScan consists in detecting clusters based on the density of points, using two parameters:
            \begin{itemize}
                \item $\varepsilon$: A distance threshold under which two points are considered close enough to be considered neighbours;   
                \item $n_{\text{min}}$: The shortest number of neighbours a points needs to have to be considered as a core point of a cluster.
            \end{itemize}

>>>>

        Firstly, only one provider is considered because a BS from provider A can't be considered as a neighbour of BS from provider B.
        Consequently, we have chosen \emph{Orange} because it is the one that has the largest number of BS.

@@

\section{Overview of use methods\label{sec:overview}}
    \subsection{Finding potential neighbours}
        When looking for neighbours, at first, a list of potential neighbours for each point is necessary.
        For that, a neighbouring graph is constructed, where the set of nodes $P$ is composed of all the selected base stations and each edge in this graph represents a neighbouring relation.

        \subsubsection{$k$-NN graph}
            The most intuitive method to do so is to connect each point to its $k$ nearest neighbours, where $k \in \mathbb{N}^*$ is a parameter to be set up.

@@

    \subsection{Finding real neighbours}
        For the purpose of our experiments, i.e. finding BS neighbours, the previously presented methods are not sufficient to find real neighbours. In fact, as said before, base stations are subject to physical constraints that need to be taken into account.

        As a consequence, some neighbouring connexions needs to be suppressed via several criteria\cite{patent_neighs}.
        \subsubsection{Distance criterion}
            A BS does not have an infinite coverage area.
            As a consequence, each edge in $U$ that is longer than a certain value, called \emph{max\_distance}, is suppressed.

@@

    \subsection{Density-based clustering methods}
        As explained later on the paper, we need to be able to assess the density of base stations, we therefore need density based clustering methods.
        \subsubsection{DBScan}
            DBScan consists in detecting clusters based on the density of points, using two parameters:
            \begin{itemize}
                \item $\varepsilon$: A distance threshold under which two points are considered close enough to be considered neighbours;   
                \item $n_{\text{min}}$: The shortest number of neighbours a points needs to have to be considered as a core point of a cluster.
            \end{itemize}
